Missing data: a simple introduction

### 2020-02-28 Draft1.tex
Minor changes

@@

	\subsection{Does imputation yield valid inference?}
	Techniques are based on the bayesian paradigm, but

	Rubin (1996) defines the term scientific estimand as the objects we wish to draw inference about. He defines them thusly: "... a quantity of scientific
	interest that can be calculated in the population and does
	not change its value depending on the data collection de-
	sign used to measure it (i.e., it does not vary with sample
	size and survey design, or the number of nonrespondents,
	or follow-up effort. Sci-
	entific estimands include population means, variances, cor-
	relations, factor loadings, regression coefficients, and these
	quantities within strata or domains, but exclude the sam-
	pling variance of a sample mean under a particular sampling
	plan and the expectation of the complete-data sample mean
	when missing values are filled in with zero or the observed sample mean. ". Rubin goes on to describe statistical validity for scientific estimands as the following: " point estimation must be approximately unbi-
	ased for the scientific estimands, averaging over the sam-
	pling and the posited nonresponse mechanisms (e.g., filling
	in zeros or means is not generally acceptable)." and "in-
	terval estimation and hypothesis testing must be valid in
	the sense that nominal levels describe operating character-
	istics over sampling and posited response mechanisms.". The latter criteria can be further refined into "randomization validity" and "confidence validity". The first is that, according to Rubin (1996),  "randomization validity means that, for interval estimates,
	"actual interval coverage = nominal interval coverage," and
	for tests of hypotheses, "actual rejection rate = nominal re-
	jection rate."  Randomization validity is of course desireable, but not always achievable, and so Rubin introduces confidence validity as a looser criterion and defines it as "hat for interval estimates, "ac-
	tual interval coverage > nominal interval coverage," and for
	tests of hypotheses, "actual rejection rate < nominal rejec-
	tion rate.""

@@

@@

>>>>

	The more advanced model based approaches of this paper uses both the Bayesian and frequentist paradigms in complementary ways. The Bayesian approach creates procedures, while the frequentist one evalueates them.

	\subsection{What is valid inference?}
	Techniques are based on the bayesian paradigm, but inference is often done in the frequentist one.

	Rubin (1996) defines the term scientific estimand as the objects we wish to draw inference about. He defines them thusly: "... a quantity of scientific
	interest that can be calculated in the population and does
	not change its value depending on the data collection de-
	sign used to measure it (i.e., it does not vary with sample
	size and survey design, or the number of nonrespondents,
	or follow-up effort. Sci-
	entific estimands include population means, variances, cor-
	relations, factor loadings, regression coefficients, and these
	quantities within strata or domains, but exclude the sam-
	pling variance of a sample mean under a particular sampling
	plan and the expectation of the complete-data sample mean
	when missing values are filled in with zero or the observed sample mean. ". Rubin goes on to describe statistical validity for scientific estimands as the following: " point estimation must be approximately unbi-
	ased for the scientific estimands, averaging over the sam-
	pling and the posited nonresponse mechanisms (e.g., filling
	in zeros or means is not generally acceptable)." and "in-
	terval estimation and hypothesis testing must be valid in
	the sense that nominal levels describe operating character-
	istics over sampling and posited response mechanisms.". The latter criteria can be further refined into "randomization validity" and "confidence validity". The first is that, according to Rubin (1996),  "randomization validity means that, for interval estimates,
	"actual interval coverage = nominal interval coverage," and
	for tests of hypotheses, "actual rejection rate = nominal re-
	jection rate."  Randomization validity is of course desireable, but not always achievable, and so Rubin introduces confidence validity as a looser criterion and defines it as "hat for interval estimates, "ac-
	tual interval coverage >= nominal interval coverage," and for
	tests of hypotheses, "actual rejection rate =< nominal rejec-
	tion rate."" We therefore proceed in our analysis of methods using these definitions when evaluating the inferential validity of imputation methods.

@@

@@

	Even Rubin (1996) admits that MI

@@

	%Remember to use Rubin's definitons of statistical validity in evaluating the methods.
